---
title: 'Lab7: Multiple linear regression intro'
author: "Narjes Mathlouthi"
date: "11/9/2021"
output: html_document
---

```{r setup, include=FALSE, message = FALSE,  warning= FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,  warning= FALSE)


library(tidyverse)
library(palmerpenguins)
library(modelsummary)
library(broom)
library(stargazer)
library(GGally)

```


## Explore penguins

Use `GGally::ggpairs` to create a pairs plot

```{r}
ggpairs(penguins)

#shows different relationships
#categorical it shows the coount within each group

#continous it will split out the vars by species ?

#it shows scatter plot relationships
```


Let's simplify the variables that we include in our ggpairs plot :

-species
-bill_length_mm through body_mass_g


```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))
#get more insights about relationships between vars
# ggpairs is just a wraper around ggplot

```


## Multiple linear regression

We are going to understand (a bit better) relationships between multiple predictor variables and an outcome which is penguin body mass  

- species
- flipper length
- sex
- bill depth

### Model1

Mode body mass based on only flipper length and bill depth
(bad idea ...there are important variables missing)

```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

#model running not an indication of success

#Call model by name to return only coefficients

model_1
summary(model_1)

#p-value is one piece of information of the model but not enough
# we could check teh R^2
#Use adjusted R^2 
```

Holding all else constant, we expect that for each 1 mm increase in flipper length, we expect that on average  body mass will increase by 51.54g.

76 % variance in penguin body mass (g) by penguin flipper length (mm) and bill depth(mm) (or say explained by the model is there are many vars).(76% value of R^2 doesn't mean much here)

Actually -- we think that a model for penguin body mass should contain variables species, flipper length, and penguin sex.




```{r}
model_2 <- lm(body_mass_g ~ species+ flipper_length_mm + sex, data = penguins)

#order doesnt matter

#Let's check out the coefficients
model_2

#Adelie is the dummy variable (0) with only zeros
#female is the dummy variable (0)
```
Interpretring coefficients for flipper_length, gentoo and and male

Holding all else constant, on average we expect  the difference in body mass (g) between Gentoo penguin  and Adelie penguin to be 836.26 g 

Holding all else constant, on average we expect the difference in body mass (g) between a male penguin's  and female to be 530.38 g 


## Visualize this model

```{r}
ggplot(data = penguins, aes(flipper_length_mm, y = body_mass_g)) + geom_point(aes(color = species)) +
  facet_wrap(~sex)
```
Try to write inline code that spits out the coefficients for Gentoo
`r penguin_model2_coef$estimate[3]`

```{r}
penguin_model2_coef <- tidy(model_2)
penguin_model2_coef 
```
Try to write inline code that spits out the coefficients for Gentoo
`r penguin_model2_coef$estimate[3]`

## Look at model diagnostics
Use the plot()
Check for homodesciticity
Normal QQ residuals are normally distributed



```{r}
plot(model_2)
summary(model_2)
```

## Report the model outputs in a summary table

```{r}
modelsummary(model_2)
```
Use stargazer :

```{r, results='asis'}
stargazer(model_2, model_1, type ="html")

```

